\chapter{Analysis}

\section{Introduction}
 
\subsection{Client Identification}
My client is Kai Leddy; He is 23 years old, he has a lot of experience working with computers for many tasks including software development.\par
Kai works for ESL which is the largest eSports organisation and league. ESL supports over 50 games and runs a number of large tournaments every month. Kai's work focuses on the tournaments for the game Counter Strike: Global Offensive. He helps to organize and run multiple large scale tournaments every year and assists with the creation of the tournament bracket. During the tournament he helps with the production of the show which includes displaying the map vetos as they are happening and showing live stats during the game.\par
Kai feels like the current systems that are being used within the company are slow, confusing and outdated and would like to test a new system to help improve efficiency.

\subsection{Define the current system}
The current system that is used to organise and run tournaments varies depending on the size and location of the tournament. All the current system involves the use of multiple programs and methods. One current system used in smaller venues involves an organiser getting the map vetos from the players and writing it down on a piece of paper which then needs to be taken to both the graphics department and the casting desk. This system has caused delays in the past and often causes confusion. Another system for map vetos that is used is only available at the largest of tournaments with only ~2 per year being able to use this system.\par
The current system for tournament bracket creation currently depends on the tournament format and how teams qualified for the tournament. For example a tournament which teams qualified for via an online tournament would have the place teams in the bracket based on their matches and result on the qualifier whereas a tournament where all teams are invited would place teams either randomly or based on a world ranking system.

\subsection{Describe the problems}
\begin{itemize}
	\item \textbf{Use of multiple systems}  - Often causes confusion and each system has it's own pros and cons. Having one system would simplify the process and allow for one system to be continually updated and benefit all events.
	\item \textbf{Lack of communication} - Current systems rely on somebody running from the team room where the veto happens to the production room and then to the casters to deliver the map vetos. This process takes time and has caused issues with people not receiving the information at all.
	\item \textbf{Lack of standardised format} - When map vetos are written on a piece of  paper the format can change due to which admin is doing the veto as well as their handwriting. There have been issues in the past with production being unable to read the veto and getting the order wrong due to the format.
	\item \textbf{Lack of live stats} - The current system relies on the gaming observer to open the scoreboard in game which only has a minimal amount. There is currently no way for production to have live stats they can display on screen.
\end{itemize}

\subsection{Section appendix}
%Interview with client notes

\section{Investigation}

\subsection{The current system}

\subsubsection{Data sources and destinations}
In the current system there are two main data sources, the tournament organisers and the teams playing. The organisers will set the map pool, format and tournament bracket and will pass this data onto the teams first to confirm the details and then release the details to the viewers
\begin{center}

\begin{tabular}{|l|l|l|l|}

    \hline
    \textbf{Source} & \textbf{Data} & \textbf{Example Data} & \textbf{Destination} \\ \hline
     Tournament Organisers & Map pool & Dust 2, Train etc.. & Viewer,Production,Teams \\ \hline
     Tournament Organisers & Tournament format  & Bo3,BBPPBBP & Viewers,Production,Teams\\ \hline
     Teams & Map veto & Team1 bans Inferno & Viewers,Production  \\ \hline
     Ingame Observer & Player Stats & OlofM 13-2-4 & Database \\
    \hline
	
\end{tabular}
%\label{tab:range_examples}

%\setlength{\tabcolsep}{13.5pt}
%\begin{tabular}{|l|l|l|l|}
%    \hline
%    \textbf{Source} & \textbf{Data} & \textbf{Example Data} & \textbf{Destination} \\ \hline
%     User                & Map pool & Dust 2 & Program/Report \\ \hline
%     User & Tournament format  & Bo3,BBPPBBP & Program/Report \\ \hline
%     Teams & Map veto & Team1 bans Inferno & Program/Report/Production  \\ \hline
%     Ebot & Player x kill & .... & Database \\
%    \hline
%\end{tabular}
%\label{tab:range_examples}
\end{center}

\subsubsection{Algorithms}

%\begin{algorithm}[H]
%\label{fig:repeat_as_while_pseudo_example_2}
%    \caption{While Loop Representation}
%\begin{algorithmic}[1]
%\SET{$veto\_complete$}{$False$}
%\SET{$maps\_playing$}{$ $}
%\State
%\While{$veto\_complete = False$}
%    \For{$(Len(map\_pool)-1)/2$}
%    
%    \If{$format\_stage = Ban$}
%        \SET{$map\_pool$}{$map\_pool - \textbf{USERINPUT} $}
%    \ElsIf{$format\_stage = Pick$}
%    	\SET{$maps\_playing$}{$\textbf{USERINPUT}$}
%    \Else
%    	\SET{$maps\_playing$}{Random from remaining}
%    \EndIf
%\EndWhile
%\end{algorithmic}
%\end{algorithm}


\subsubsection{Data flow diagram}

\subsubsection{Input Forms, Output Forms, Report Formats}

\subsection{The proposed system}

\subsubsection{Data sources and destinations}

\subsubsection{Data flow diagram}
	%create from paper version
\subsubsection{Data dictionary}
\begin{center}
	\begin{tabular}{|l|l|l|l|p{2.5cm}|l|}
	\hline
	\textbf{Name}&\textbf{Data type}&\textbf{Length}&\textbf{Validation}&\textbf{Example Data}&\textbf{Comment} \\ \hline
	TeamID&Interger&1-255&Range&3& \\ \hline
	TeamName&String&3-32 Characters & Length & Fnatic & \\ \hline
	TeamNationality&String&2-32 Characters & Length & Sweedish & \\ \hline
	TeamCoach&String&4-32 Characters & Length & Vuggo & \\ \hline
	TeamRanking&Interger&1-255&Range&1& \\ \hline
	TeamYearFounded%String%4 Charcters & Length & 2004 & \\ \hline
	TournamentID & Interger&1-255&Range&1& \\ \hline
	TournamentVenue & String & 2-32 Characters&Length& Polyvalent Hall& \\ \hline
	TournamentCity & String & 3-16&Length&Cluj-Napoca& \\ \hline
	TournamentCountry&String&2-16&Length&Romanina& \\ \hline
	TournamentNoOfTeams&Interger&4-64&Range&16& \\ \hline
	TournamentFormat&String&4-255&Length&Groups + Single elimination& \\ \hline
	MatchID&Interger&1-1000&Range&4& \\ \hline

	
\end{tabular}
\end{center}
\subsubsection{Volumetrics}

\section{Objectives}

\subsection{General Objectives}

\subsection{Specific Objectives}

\subsection{Core Objectives}

\subsection{Other Objectives}

\section{ER Diagrams and Descriptions}

\subsection{ER Diagram}

\subsection{Entity Descriptions}

\section{Object Analysis}

\subsection{Object Listing}

\subsection{Relationship diagrams}

\subsection{Class definitions}

\section{Other Abstractions and Graphs}

\section{Constraints}

\subsection{Hardware}

\subsection{Software}

\subsection{Time}

\subsection{User Knowledge}

\subsection{Access restrictions}

\section{Limitations}

\subsection{Areas which will not be included in computerisation}

\subsection{Areas considered for future computerisation}

\section{Solutions}

\subsection{Alternative solutions}

\subsection{Justification of chosen solution}
